%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\itemsep}{5pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\classesList}[4]{
	\item\small{
		{#1 #2 #3 #4 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{\large#1} & \textbf{\small #2} \\
		\textit{\large#3} & \textit{\small #4} \\

	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & \textbf{\small #2}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
		\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
		\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
	{\Huge \scshape Nam Anh Pham Hoang (Harris)} \\ \vspace{1pt}
	Ho Chi Minh City, Vietnam \\ \vspace{1pt}
	\small \href{tel:+84 869 481 840}{ \raisebox{-0.1\height}\faPhone\ \underline{+84 869 481 840} ~}
	\href{mailto:phnanh.harris@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{phnanh.harris@gmail.com}} ~
	\href{https://linkedin.com/in/phnaharris}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{phnaharris}}  ~
	\href{https://github.com/phnaharris}{\raisebox{-0.2\height}\faGithub\ \underline{phnaharris}} ~
	\href{https://phnaharris.github.io}{\raisebox{-0.2\height}\faGlobe\  \underline{https://phnaharris.github.io}} ~
\end{center}
\vspace{-8pt}


%-----------EDUCATION-----------
\vspace{-8pt}
\section{EDUCATION}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading
{VNUHCM - University of Science}{2018 -- 2022}
{Bachelor's degree (Computer Science major)}{Ho Chi Minh City, Vietnam}
\resumeSubHeadingListEnd
\vspace{-8pt}


%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
\begin{multicols}{4}
	\resumeItemListStart
	\resumeItem{Data Structures \& Algorithms}
	\resumeItem{Mobile Application Development}
	\resumeItem{Database Management System (DBMS)}
	\resumeItem{Web API Application Development}
	\resumeItem{Operating Systems}
	\resumeItem{Computer Sciences}
	\resumeItem{OOPs Concept}
	\resumeItem{Blockchain}
	\resumeItem{Distributed System}
	\resumeItem{Cryptography}
	\resumeItem{Consensus}
	\resumeItemListEnd
\end{multicols}


%-----------EXPERIENCE-----------
\section{WORKING EXPERIENCE}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading
{Beowulf Blockchain \href{https://beowulfchain.com/}{\raisebox{-0.1\height}\faExternalLink}}{06 2022 -- Present}
{\underline{Blockchain Developer}}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\vspace{1pt}
\resumeItem{\normalsize{Responsible for the development, deployment, and maintenance of smart contracts on a variety of networks and protocols}}
\resumeItem{\normalsize{Develop a suite of web3 services using a variety of technologies, including Rust, Node.js, Solidity, and IPFS}}
\resumeItem{\normalsize{Backend Developer with Rust, Node.js}}
\vspace{1pt}
\resumeItemListEnd

\vspace{5pt}

\resumeSubheading
{Freelancer \href{https://phnaharris.github.io}{\raisebox{-0.1\height}\faExternalLink}}{08 2019 -- 06 2021}
{\underline{Mobile Application Developer}}{Vietnam}
\resumeItemListStart
\vspace{1pt}
\resumeItem{\normalsize{Study a variety of .NET Framework technical stack, including ASP.NET MVC, WPF, Entity Framework, and Xamarin.Forms}}
\resumeItem{\normalsize{Communicate effectively with customers and team leaders to understand their needs and build applications that serves those needs}}
\resumeItem{\normalsize{Support customers to use and maintain the product}}
\resumeItem{\normalsize{Built Web API using ASP.NET MVC and Entity Framework }}
\resumeItem{\normalsize{Built mobile cross-platform application using Xamarin.Forms}}
\resumeItem{\normalsize{Built automation tool with Selenium and WPF to improve the user interaction with the application}}
\vspace{1pt}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\vspace{5pt}
\resumeItemListStart
\resumeItem{\textbf{\normalsize{Languages: }}{\normalsize{Rust, JavaScript/TypeScript,
			Golang, C\#, C/C++,  Python, Solidity, Bash, Lua...}}}

\resumeItem{\textbf{\normalsize{DBMS: }}{\normalsize{MongoDB, PostgreSQL, MySQL, SQLite,...}}}

\resumeItem{\textbf{\normalsize{Developer Tools: }}{\normalsize{Arch Linux,
			Neovim, Hyprland Window Manager, Visual Studio, Remix, Android Studio, Postman, ngrok.io...}}}
\resumeItem{\textbf{\normalsize{Technologies/Frameworks: }}{\normalsize{Axum, Rocket.rs (Rust),
			Express.js, Fastify, Astro.js (Node.js), Xamarin.Forms with MVVM pattern, ASP.NET MVC with Entity Framework,
			WPF, Selenium,...}}}
\resumeItem{\textbf{\normalsize{CI/CD: }}{\normalsize{Github Actions, Ansible, Linux, Docker,...}}}
\vspace{1pt}
\resumeItemListEnd
\vspace{-5pt}


%-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}
\vspace{5pt}

\resumeItemListStart
\resumeItem{\href{https://www.linkedin.com/in/phnaharris/details/skills/}{LinkedIn Skill Assessment: C\#, .NET, C/C++, T-SQL,...} \href{https://www.linkedin.com/in/phnaharris/details/skills/}{\raisebox{-0.1\height}\faExternalLink }}
\resumeItem{\href{https://www.hackerrank.com/phnaharris}{Hackerrank Certification }{\raisebox{-0.1\height}\faExternalLink}}
\resumeItemListEnd

%-----------SOFT SKILLS-----------
\section{SOFT SKILLS}
\vspace{5pt}
\resumeItemListStart
\resumeItem{\normalsize{Passionate about learning new skills for life and technology.}}
\resumeItem{\normalsize{Increase productivity by automating repetitive tasks.}}
\resumeItem{\normalsize{Good at adaptability and problem solving with new environment.}}
\resumeItem{\normalsize{Communication skill.}}
\vspace{1pt}
\resumeItemListEnd
\vspace{-5pt}


% -----------INVOLVEMENT---------------
\section{EXTRACURRICULAR}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubheading{Google IO Extended Vietnam 2019}{07 2019}
{}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\vspace{1pt}
\resumeItem{\normalsize{Certificate of Completion present for successfully completing the TensorFlow, Keras and deep learning, without a PhD. \href{https://phnaharris.github.io/assets/google-io-extended-2019/tensorflow.jpg} {\raisebox{-0.1\height}\faExternalLink}}}
\resumeItem{\normalsize{Certificate of Completion present for successfully completing the Building Beautiful UIs with Flutter. \href{https://phnaharris.github.io/assets/google-io-extended-2019/flutter.jpg} {\raisebox{-0.1\height}\faExternalLink}}}
\vspace{1pt}
\resumeItemListEnd

\vspace{5pt}

\resumeSubheading{HCMUS's BLIT Program}{2018}{}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\vspace{1pt}
\resumeItem{\normalsize{Candidate of 4th round of BLIT Competition at VNUHCM - University of Science.}}
\vspace{1pt}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{PROJECTS}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\large{IHI}} $|$ \large{Mobile Developer}}{2021}
\resumeItemListStart
\resumeItem{\normalsize{The app provides online teaching service for student with
		variety of subjects. With this app, student can purchase courses
		from our partners, study online and review their knowledge with
		our exercise. By using IHI, student can study from everywhere
		they want and with their speed at specific lesson, easily check
		their understanding just with a device which have Internet connection.}}

\resumeItem{\normalsize{Tech stack: Xamarin.Forms with MVVM pattern, HttpRequest, payment process
		with Momo, ASP.NET MVC Web API with Entity Framework.}}

% \resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{\large{Automatic streaming tool}} $|$ \large{Developer}}{2021}
\resumeItemListStart
\resumeItem{\normalsize{The automatic tool that allow user to create, edit,
		remove video stream on Youtube. User can create
		Chrome profile associated with Google account,
		choose video you want to stream on Youtube, setup start
		time and end time of that live stream. When the tool
		streaming, user can see quality of that video stream (by
		bitrate, FPS, speed) and buy amount of viewers by third
		party service. User can stream on more than one Google
		account at a time.}}

\resumeItem{\normalsize{Tech stack: WPF, Selenium with Chrome profile
		interaction, multithreading architecture, Youtube
		streaming with FFMPEG, WinAPI (Process).}}

%\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}


\resumeProjectHeading
{\textbf{\large{Gamvip account checking tool}} $|$ \large{Developer}}{2021}
\resumeItemListStart
\resumeItem{\normalsize{The automatic tool that allow user to load a list of gamvip (a list
		of webgame) account, log in and request account information
		like name, user id, financial information.... User can use
		multithreading architecture to improve tool performance.}}

\resumeItem{\normalsize{Tech stack: WPF, HttpRequest, multithreading architecture.}}

% \resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{\large{Yahoo account checking tool}} $|$ \large{Developer}}{2020}
\resumeItemListStart
\resumeItem{\normalsize{The automatic tool that allow user to load a list of outlook
		email (hotmail and password), check if that email have
		yahoo account linked, save the yahoo account and use
		that account to get account uid and reset a
		corresponding facebook account password. User can
		use multithreading architecture to improve tool
		performance.}}

\resumeItem{\normalsize{Tech stack: WPF, Selenium, multithreading architecture,
		regular expression, mail service library, bypass captcha
		service library, HttpRequest.}}

%\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{\large{Order filtering tool}} $|$ \large{Developer}}{2020}
\resumeItemListStart
\resumeItem{\normalsize{The automatic tool that getting all of orders confirmation
		email (email \& password provided), checking and
		filtering details such as color, size, customer information
		(phone, address, email, ...), ... add that details into excel
		files.}}

\resumeItem{\normalsize{Tech stack: WPF, Selenium, multithreading architecture,
		regular expression, mail service library.}}

%5\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{\large{Spotify password changing tool}} $|$ \large{Developer}}{2020}
\resumeItemListStart
\resumeItem{\normalsize{The automatic tool that allow user to load a list of Spotify
		account with its changing password link. The tool follow the link
		automatically, enter password and new password, bypass
		captcha and submit. User can use multithreading architecture
		to improve tool performance.}}

\resumeItem{\normalsize{Tech stack: WPF, HttpRequest, multithreading architecture, Selenium.}}

%\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\pagebreak

\resumeProjectHeading
{\textbf{\large{Seanato}} $|$ \large{Mobile Developer}}{2019}
\resumeItemListStart
\resumeItem{\normalsize{The app provides ferry booking, cable car tickets, tickets
		to amusement parks of Vinpearl and Sun World.
		\\Seanato is the first and only application that provides a
		ticketing service in the field of maritime tourism, linking
		most of the major ferry carriers in the Kien Giang province
		to provide customers with optimal choice and the most
		effective.
		\\Seanato also cooperates with Vietnam's major travel groups such as Vingroup, Sun World.}}

\resumeItem{\normalsize{Tech stack: Xamarin.Forms with MVVM pattern, HttpRequest, payment
		process with Momo \& Alepay...}}

%\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading
{\textbf{\large{Pong game}} $|$ \large{Teamlead, Developer}}{2019}
\resumeItemListStart
\resumeItem{\normalsize{Pong game is my end-of-term project of Programming
		Engineering term at university that use basic skill with C++
		programming language.}}

\resumeItem{\normalsize{Tech stack: C++ programming language.}}

\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
\resumeItemListEnd
\vspace{-13pt}





% \resumeProjectHeading
%     {{\textbf{\large{\underline{Project Name}}}} $|$ \large{Technology Stack Used}}{2021}
%     \resumeItemListStart
%       \resumeItem{\normalsize{About project \textbf{highlight key points}.}}
%       \resumeItem{\textcolor{accent} {\href{Project Link} {\underline{\normalsize{Download}}}}}
%     \resumeItemListEnd
%     \vspace{-13pt}
\resumeSubHeadingListEnd
\vspace{-12pt}

\end{document}
